Output Summary

### 2021-08-03 03-post-process/output-plots.Rmd
Update front matter of output-plots for multi-population model

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'MIN' = 'Minam', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

@@

# read information from this model
model_info = readRDS(file.path(in_dir, paste0(params$pop, "-output-", params$scenario, ".rds")))

@@

# which years are "observable"?
observable = (jags_data$kmax+1):jags_data$ny
```

>>>>

---
title: "Output Summary"
subtitle: "Multi-Population Model"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  scenario:
    label: "Scenario"
    value: "base"
    input: text
editor_options: 
  chunk_output_type: console
---

@@

# read information from this model
model_info = readRDS(file.path(in_dir, paste0(params$pop, "output-", params$scenario, ".rds")))

@@

# the years included by the model
all_yrs = as.numeric(dimnames(jags_data$Pa_obs)[[1]])

# which years are "observable" for at least some quantities?
observable = (jags_data$kmax+1):jags_data$ny
```
